Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-18 paper/main.tex
Tune BA plot description

% intro
Third, we inspected results from both naturalistic paradigms on the level of
individual participants, and compared them to the individual PPA localizations
provided by \cite{sengupta2016extension}, who reported
% Sengupta et al., 2016; unilateral in sub-04 and sub-20
bilateral parahippocampal clusters in 12 of 14
participants and a unilateral right clusters in two participants
\citep[Tab.~3 in][]{sengupta2016extension}.
% one contrast to localize them all; "...and $Z$>3.4 for all"
Unlike \cite{sengupta2016extension}, who determined PPA clusters using three
candidate contrasts and a variable threshold, we used a single contrast for
each naturalistic stimulus and a uniform threshold for all participants.
% subject space -> NeuroVault
Results of the analyses that were performed in participant-space can be found in the
accompanying dataset ($Z$>2.3, $p$<.05 cluster-corrected).
% here report in group space
For better comparisons of participants, we here report results from the analyses
performed in group space ($Z$>3.4, $p$<.05 cluster-corrected).
% ref to figure
Figure~\ref{fig:subs-thresh-ppa} depicts thresholded $Z$-maps of the primary movie
and audio-description $t$-contrast, and the outline of overlapped, individual PPAs
co-registered to the MNI152 template.
% one slice to show them all
Transversal slice of $Z$=-11 was chosen as it depicts voxels of
significant clusters in almost all participants.

% AV
Results of the primary movie contrast yielded bilateral clusters in five participants,
a unilateral right cluster in six participants (of which one participant yielded a
unilateral cluster in the visual localizer), and a unilateral left cluster in
one participant.
% difference to dedicated localizer
We find homologous clusters in sub-20, whereas the dedicated visual localizer
yielded only one cluster in the right hemisphere.

% report here in group
Results of the primary audio-description contrast yielded bilateral clusters in nine participants
that are within or overlapping with the individual PPA.
% subj-04
In sub-04, two homologous clusters are apparent, whereas the dedicated localizer
(and movie stimulus) yielded only one cluster in the right hemisphere.
% sub-09
In sub-09 the analysis yielded one cluster in the left-hemispheric PPA.

@@

% Bland-Altman-Plots
To better depict the agreement and difference between the results of the visual
localizer and the primary audio-description contrast, we created a Bland-Altman-Plot for every
participant (Fig.~\ref{fig:bland-altman}).
% what it depicts
Each subplot visualizes the mean value and difference (localizer minus audio-description) of
two spatially corresponding voxels in the unthresholded $Z$-maps.
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (cf. KDE plot for the x-axes).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $Z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show a higher $Z$-value in the audio-description stimulus.

@@

>>>>

% intro
Third, we inspected results from both naturalistic paradigms on the level of
individual participants, and compared them to the individual PPA localizations
provided by \cite{sengupta2016extension}, who reported
% Sengupta et al., 2016; unilateral in sub-04 and sub-20
bilateral parahippocampal clusters in 12 of 14
participants and a unilateral right clusters in two participants
\citep[Tab.~3 in][]{sengupta2016extension}.
% one contrast to localize them all; "...and $Z$>3.4 for all"
Unlike \cite{sengupta2016extension}, who determined PPA clusters using three
candidate contrasts and a variable threshold, we used a single contrast for
each naturalistic stimulus and a uniform threshold for all participants.
% ref to figure
Figure~\ref{fig:subs-thresh-ppa} depicts thresholded $Z$-maps of the primary movie
and audio-description $t$-contrasts, in comparison to the results of a conventional
block-design localizer (unthresholded $Z$-maps are provided on NeuroVault).
% AV
Results of the primary movie contrast yielded bilateral clusters in five participants,
a unilateral right cluster in six participants (of which one participant yielded a
unilateral cluster in the visual localizer), and a unilateral left cluster in
one participant.
% difference to dedicated localizer
We find bilateral clusters for participant \texttt{sub-20}, whereas the block-design
localizer yielded only one cluster in the right hemisphere.
% report here in group
Results of the primary audio-description contrast yielded bilateral clusters in nine participants that are within or overlapping with the block-design localizer results.
% subj-04
In participant \texttt{sub-04}, two bilateral clusters are apparent, whereas
block-design localizer, and movie stimulus yielded only one cluster in the right
hemisphere.
% sub-09
For another participant (\texttt{sub-09}) the analysis yielded one cluster in the
left-hemispheric PPA.

@@

% Bland-Altman-Plots
To illustrate the similarity of correlates of spatial processing in
naturalistic (audio-description) and conventional stimulation, independent of a
particular cluster-forming threshold, Bland-Altman plots for all participants
are shown in Figure.~\ref{fig:bland-altman}).
% what it depicts
Each subplot visualizes the mean value and difference (localizer minus audio-description) of all voxels in temporal and occipital cortices. The marginal distributions
of the mean scores indicate a general agreement of both contrast scores across
voxels in the PPA localization overlap as a probabilistic indicator (blue), and the
individual block-design localizer results (red). Notably, 11 participants exhibit
a pattern of increased $Z$-scores for the naturalistic stimulus (lower right
quadrant) that includes voxels labeled by the block-design localizer, but
also additional voxels.

@@

% subject space -> NeuroVault
Results of the analyses that were performed in participant-space can be found in the
accompanying dataset ($Z$>2.3, $p$<.05 cluster-corrected).
